Bird beak's elaboration and exploration

### 2021-06-04 Analysis/03-elaboration_exploration_analyses.Rmd
Up

Finaly, we also looked at the exploration elaboration profiles within each clades by replacing for each clade, the projection of the elements onto $\vec{B}$ to the projection onto their respective clade major axes $\vec{a}$.

@@

>>>>

Finally, we also looked at the exploration elaboration profiles within each clades by replacing for each clade, the projection of the elements onto $\vec{B}$ to the projection onto their respective clade major axes $\vec{a}$.

@@

But this is probably best to look at in a species by species fashion:

TODO
